Brief notes on erosion

### 2019-05-21 docs/proposals/ErosionWhitePaper.tex
NM

  \item {\bf Interface Tracking}: We describe the interface using
  {\thL} coordinates, where $\theta$ is a local tangent angle, and $L$
  is the total interface length.  In these coordinates, the
  stiff terms are linear and are be discretized implicitly.

  \item {\bf Validation}: We compare the numerical simulations with
  scaling laws.
\end{enumerate}

\section{Proposed Work}
Having developed and validated numerical methods for simulating viscous
erosion, there are two main directions that our research will follow.
First, {\bf additional numerical tools are required to simulate more
realistic scenarios such as denser packings, transport, and
three-dimensional erosion}.  Second, {\bf we will investigate physically
motivated questions regarding the geometry and flow inside an eroding
porous medium}.

>>>>

  \item {\bf Interface Tracking}: We describe the interface using
  {\thL} coordinates, where $\theta$ is a local tangent angle, and $L$
  is the total interface length.  In these coordinates, the
  stiff terms are linear which allows implicit methods to be used for time discretization.

  \item {\bf Validation}: We compare the numerical simulations against analytical predictions for the limiting shape of a single body and scaling laws for its vanishing rate.
\end{enumerate}

\section{Proposed Work}
Having developed and validated numerical methods for simulating viscous
erosion, there are two main directions that our research will follow.
First, {\bf additional numerical tools are required to simulate more
realistic scenarios such as denser packings, transport, and
three-dimensional erosion}.  Second, {\bf we will investigate physically
motivated questions regarding the reconfiguration of geometry and flow inside an eroding
porous medium}.
